---
title: "Comparing Two Tasks"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(warning = FALSE, message = FALSE) 
library(ggplot2)
library(ggExtra)
library(ggalt)
library(plotly)
library(cluster)
library(factoextra)
data <- read.csv(file="./data.csv")
data_unlabelled <- data[3:4]
data_scaled <- scale(data_unlabelled)
data_scaled_names <- cbind(data[1:4],data_scaled)
names(data_scaled_names)[5] <- 'task1_zscore'
names(data_scaled_names)[6] <- 'task2_zscore'
```

```{r echo=FALSE}
excellent <- 1.5
increase <- 1
decrease <- 1
poor <- -1.5
```

## Cohort Results

```{r echo=FALSE}
theme_set(theme_bw())
y9all <- ggplot(data, aes(task1, task2, color = class, label = name)) + 
  geom_point(size=1, alpha=1/2) +
  geom_encircle(data=subset(data_scaled_names, (task1_zscore+task2_zscore)/2>excellent), colour="#00AA00", fill="#00AA0022", spread=0.01) +
  geom_encircle(data=subset(data_scaled_names, (task2_zscore-task1_zscore)>increase), colour="#0000AA", fill="#0000AA22", spread=0.01) +
  geom_encircle(data=subset(data_scaled_names, (task1_zscore-task2_zscore)>decrease), colour="#AA0000", fill="#AA000022", spread=0.01) +
  geom_encircle(data=subset(data_scaled_names, (task1_zscore+task2_zscore)/2<poor), colour="#FF0000", fill="#FF000022", spread=0.01) +
  xlim(0, 100) +
  ylim(0, 100)
ggMarginal(y9all,, groupColour = TRUE, groupFill = TRUE)
```

<span style="color:#00AA00">Students with an average z-score above `r excellent`</span>
```{r echo=FALSE}
goodz1 <- subset(data_scaled_names, (task1_zscore+task2_zscore)/2>excellent)
goodz1
```

<span style="color:#0000AA">Students who increased by a z-score of `r increase` or more</span>
```{r echo=FALSE}
improvez1 <- subset(data_scaled_names, (task2_zscore-task1_zscore)>increase)
improvez1
```

<span style="color:#AA0000">Students who decreased by a z-score of `r decrease` or more</span>
```{r echo=FALSE}
worsez1 <- subset(data_scaled_names, (task1_zscore-task2_zscore)>=increase)
worsez1
```

<span style="color:#FF0000">Students with an average z-score below `r poor`</span>
```{r echo=FALSE}
poorz1 <- subset(data_scaled_names, (task1_zscore+task2_zscore)/2<poor)
poorz1
```

### Interactive Chart
```{r echo=FALSE}
INT <- 
  ggplot(data, aes(task1, task2, color = class)) + 
  geom_point(size=1, aes(text=name), alpha=1/2) +
  theme_bw() + 
  geom_segment(aes(x = 0, y = 0, xend = 100, yend = 100), color="black", linetype=1, size=.25)

ggplotly(INT) %>% config(displayModeBar = F)
```

## Clustered Groups {.tabset .tabset-fade}

### 2 Clusters {.tabset .tabset-pills}

```{r echo=FALSE}
data.labels = data$class
data_unlabelled <- data[3:4]
data_scaled <- scale(data_unlabelled)
km.out <- kmeans(data_scaled, centers=2, nstart=100)
km.clusters <- km.out$cluster
rownames(data_scaled) <- paste(data$name, 1:dim(data)[1], sep = "_")
fviz_cluster(list(data=data_scaled, cluster = km.clusters),show.clust.cent = FALSE, labelsize = 0, repel= TRUE)
final_data <- cbind(data, cluster = km.clusters)
sorted_data <- final_data[order(final_data$cluster),] 
table(km.clusters)
```

#### Hide

#### Show

```{r echo=FALSE}
a2 <- c(subset(sorted_data, cluster==1)[2])
b2 <- c(subset(sorted_data, cluster==2)[2])
list(a2, b2)
```

### 3 Clusters {.tabset .tabset-pills}

```{r echo=FALSE}
data.labels = data$class
data_unlabelled <- data[3:4]
data_scaled <- scale(data_unlabelled)
km.out <- kmeans(data_scaled, centers=3, nstart=100)
km.clusters <- km.out$cluster
rownames(data_scaled) <- paste(data$name, 1:dim(data)[1], sep = "_")
fviz_cluster(list(data=data_scaled, cluster = km.clusters),show.clust.cent = FALSE, labelsize = 0, repel= TRUE)
final_data <- cbind(data, cluster = km.clusters)
sorted_data <- final_data[order(final_data$cluster),] 
table(km.clusters)
```

#### Hide

#### Show

```{r echo=FALSE}
a3 <- c(subset(sorted_data, cluster==1)[2])
b3 <- c(subset(sorted_data, cluster==2)[2])
c3 <- c(subset(sorted_data, cluster==3)[2])
list(a3, b3, c3)
```

### 4 Clusters {.tabset .tabset-pills}

```{r echo=FALSE}
data.labels = data$class
data_unlabelled <- data[3:4]
data_scaled <- scale(data_unlabelled)
km.out <- kmeans(data_scaled, centers=4, nstart=100)
km.clusters <- km.out$cluster
rownames(data_scaled) <- paste(data$name, 1:dim(data)[1], sep = "_")
fviz_cluster(list(data=data_scaled, cluster = km.clusters),show.clust.cent = FALSE, labelsize = 0, repel= TRUE)
final_data <- cbind(data, cluster = km.clusters)
sorted_data <- final_data[order(final_data$cluster),] 
table(km.clusters)
```

#### Hide

#### Show

```{r echo=FALSE}
a4 <- c(subset(sorted_data, cluster==1)[2])
b4 <- c(subset(sorted_data, cluster==2)[2])
c4 <- c(subset(sorted_data, cluster==3)[2])
d4 <- c(subset(sorted_data, cluster==4)[2])
list(a4, b4, c4, d4)
```

### 5 Clusters {.tabset .tabset-pills}

```{r echo=FALSE}
data.labels = data$class
data_unlabelled <- data[3:4]
data_scaled <- scale(data_unlabelled)
km.out <- kmeans(data_scaled, centers=5, nstart=100)
km.clusters <- km.out$cluster
rownames(data_scaled) <- paste(data$name, 1:dim(data)[1], sep = "_")
fviz_cluster(list(data=data_scaled, cluster = km.clusters),show.clust.cent = FALSE, labelsize = 0, repel= TRUE)
final_data <- cbind(data, cluster = km.clusters)
sorted_data <- final_data[order(final_data$cluster),] 
table(km.clusters)
```

#### Hide

#### Show

```{r echo=FALSE}
a5 <- c(subset(sorted_data, cluster==1)[2])
b5 <- c(subset(sorted_data, cluster==2)[2])
c5 <- c(subset(sorted_data, cluster==3)[2])
d5 <- c(subset(sorted_data, cluster==4)[2])
e5 <- c(subset(sorted_data, cluster==5)[2])
list(a5, b5, c5, d5, e5)
```

### 6 Clusters {.tabset .tabset-pills}

```{r echo=FALSE}
data.labels = data$class
data_unlabelled <- data[3:4]
data_scaled <- scale(data_unlabelled)
km.out <- kmeans(data_scaled, centers=6, nstart=100)
km.clusters <- km.out$cluster
rownames(data_scaled) <- paste(data$name, 1:dim(data)[1], sep = "_")
fviz_cluster(list(data=data_scaled, cluster = km.clusters),show.clust.cent = FALSE, labelsize = 0, repel= TRUE)
final_data <- cbind(data, cluster = km.clusters)
sorted_data <- final_data[order(final_data$cluster),] 
table(km.clusters)
```

#### Hide

#### Show

```{r echo=FALSE}
a6 <- c(subset(sorted_data, cluster==1)[2])
b6 <- c(subset(sorted_data, cluster==2)[2])
c6 <- c(subset(sorted_data, cluster==3)[2])
d6 <- c(subset(sorted_data, cluster==4)[2])
e6 <- c(subset(sorted_data, cluster==5)[2])
f6 <- c(subset(sorted_data, cluster==6)[2])
list(a6, b6, c6, d6, e6, f6)
```

### 7 Clusters {.tabset .tabset-pills}

```{r echo=FALSE}
data.labels = data$class
data_unlabelled <- data[3:4]
data_scaled <- scale(data_unlabelled)
km.out <- kmeans(data_scaled, centers=7, nstart=100)
km.clusters <- km.out$cluster
rownames(data_scaled) <- paste(data$name, 1:dim(data)[1], sep = "_")
fviz_cluster(list(data=data_scaled, cluster = km.clusters),show.clust.cent = FALSE, labelsize = 0, repel= TRUE)
final_data <- cbind(data, cluster = km.clusters)
sorted_data <- final_data[order(final_data$cluster),] 
table(km.clusters)
```

#### Hide

#### Show

```{r echo=FALSE}
a7 <- c(subset(sorted_data, cluster==1)[2])
b7 <- c(subset(sorted_data, cluster==2)[2])
c7 <- c(subset(sorted_data, cluster==3)[2])
d7 <- c(subset(sorted_data, cluster==4)[2])
e7 <- c(subset(sorted_data, cluster==5)[2])
f7 <- c(subset(sorted_data, cluster==6)[2])
g7 <- c(subset(sorted_data, cluster==7)[2])
list(a7, b7, c7, d7, e7, f7, g7)
```

### 8 Clusters {.tabset .tabset-pills}

```{r echo=FALSE}
data.labels = data$class
data_unlabelled <- data[3:4]
data_scaled <- scale(data_unlabelled)
km.out <- kmeans(data_scaled, centers=8, nstart=100)
km.clusters <- km.out$cluster
rownames(data_scaled) <- paste(data$name, 1:dim(data)[1], sep = "_")
fviz_cluster(list(data=data_scaled, cluster = km.clusters),show.clust.cent = FALSE, labelsize = 0, repel= TRUE)
final_data <- cbind(data, cluster = km.clusters)
sorted_data <- final_data[order(final_data$cluster),] 
table(km.clusters)
```

#### Hide

#### Show

```{r echo=FALSE}
a8 <- c(subset(sorted_data, cluster==1)[2])
b8 <- c(subset(sorted_data, cluster==2)[2])
c8 <- c(subset(sorted_data, cluster==3)[2])
d8 <- c(subset(sorted_data, cluster==4)[2])
e8 <- c(subset(sorted_data, cluster==5)[2])
f8 <- c(subset(sorted_data, cluster==6)[2])
g8 <- c(subset(sorted_data, cluster==7)[2])
h8 <- c(subset(sorted_data, cluster==8)[2])
list(a8, b8, c8, d8, e8, f8, g8, h8)
```